---
title: "gather"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(fivethirtyeight)

```

```{r}
#data_1 <- read.table("raw_data/usa_00001.dat.gz")

#View(data_1)
```
# NOTE: To load data, you must download both the extract's data and the DDI
# and also set the working directory to the folder with these files (or change the path below).

if (!require("ipumsr")) stop("Reading IPUMS data into R requires the ipumsr package. It can be installed using the following command: install.packages('ipumsr')")

ddi <- read_ipums_ddi("usa_00001.xml")
data <- read_ipums_micro(ddi)

```{r}
susp_team <- nfl_suspensions %>%
  group_by(team) %>%
  summarize(sus_count = n(), .groups = "keep") %>%
  
  #No need to filter here because the summarize only applies to the team column,
  #because that's how the groups were formed. Therefore, only team and the
  #summary column "sus_count" will be shown.
  
  filter(team != "FREE") %>% 
  
  #Filter function here filters to include only the rows NOT with team ==
  #"FREE". In this case, I think that removes the free agents who received
  #suspensions.
  
  ggplot(aes(team, sus_count)) +
  geom_col(fill = "limegreen", color = "white") +
  
  #color = "white" has the effect of spacing out the bars.
  
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90,
                                   vjust = .5,
                                   hjust = 1)) +
  
  #the theme(axis... = 1) code chunk makes the x-axis labels vertical (i.e. the
  #angle 90 degree), and vjust and hjust help to center the axis labels below
  #the respective bars
  
  labs(title = "NFL Suspensions By Team All-time",
       x = "Name of NFL Team",
       y = "Number of Suspensions")
 
  #Graph labels code chunk
 
susp_team

View(nfl_suspensions)

```

